Isomorphisms as Groupoids: \\ Homotopy Type Theory and Fractional Types

### 2013-11-18 f.tex
playing with pointed types

\begin{document}
\begin{titlepage}
\begin{center}
\vfill
{\LARGE Isomorphisms as Groupoids: \\ 
  Homotopy Type Theory and Fractional Types} \\[1.5cm]
{\Large Jacques Carette${}^*$ \qquad Amr Sabry${}^{\dagger}$}\\[0.5cm]
{\Large $({}^*)$~McMaster University \qquad $({}^\dagger)$~Indiana University}
\vfill
\end{center}
\vfill
\noindent\textbf{Abstract.}

@@

\title{Isomorphisms as Groupoids: \\ 
  Homotopy Type Theory and Fractional Types}
\author{Jacques Carette \and Amr Sabry}
\date{\today}
\maketitle

>>>>

\begin{document}
\begin{titlepage}
\begin{center}
\vfill
{\LARGE Isomorphisms as Groupoids: \\ 
  Homotopy Type Theory and Fractional Types} \\[1.5cm]
\vfill
\end{center}
\vfill
\noindent\textbf{Abstract.}

@@

\title{Isomorphisms as Groupoids: \\ 
  Homotopy Type Theory and Fractional Types}
\author{?}
\date{\today}
\maketitle
